Generalized Plackett-Luce Likelihoods

### 2022-08-16 inst/jss_hyper3.Rnw
more careful wording

which has a minimum of about $13.9$ at at about $a=0.575$.  This is
intermediate between the two-runner case where the Fisher information
exceeds 4 (minimum at $p_a=\frac{1}{2}$), and the case of three
distinct runners, where the Fisher information exceeds
$\frac{1323}{16}\simeq 82.7$ (minimum at $p_a=p_b=p_c=\frac{1}{3}$); a
brief discussion is given at \code{inst/fisher\_inf\_PL3.Rmd}.

>>>>

which has a minimum of about $13.9$ at at about $a=0.575$.  This is
intermediate between the two-runner case where the Fisher information
has a minimum of 4 at $p_a=p_b=\frac{1}{2}$, and the case of three
distinct runners $a,b,c$, where the Fisher information has a minimum
of $\frac{1323}{16}\simeq 82.7$ at $p_a=p_b=p_c=\frac{1}{3}$; a brief
discussion is given at \code{inst/fisher\_inf\_PL3.Rmd}.
